### 2018-12-21 tex/paper.tex
Introduction modified.

In this work, we establish a hitherto unknown connection between the submodular
extension of the Potts model proposed by Zhang et al.\citep{zhang2015higher}, and the
objective function of an accurate linear programming (LP) relaxation of the
corresponding MAP estimation problem~\citep{kleinberg2002approximation}. Specifically, the Lovasz extension of a submodular extension can be shown to be an objective function for the LP relaxation. This
connection has four important practical consequences. First, it establishes
the accuracy of the submodular extension of the Potts model, via the
UGC-hardness worst-case optimality of the LP relaxation. Second, it provides an
accurate submodular extension of the hierarchical Potts model, via the LP
relaxation of the corresponding MAP estimation problem proposed
by Kleinberg and Tardos \citep{kleinberg2002approximation}. Since any metric can be accurately
approximated as a mixture of hierarchical Potts
models~\citep{bartal1996probabilistic, bartal1998approximating}, this result
also provides a computationally feasible algorithm for estimating the marginals
for metric labeling. Third, it establishes the equivalence between the
subgradient of the LP relaxation and the conditional gradient of the problem of
minimising the upper bound of the log-partition. This allows us to employ the
widely used dense CRF, since the subgradient of its LP relaxation can be
efficiently computed using a recently proposed modified Gaussian filtering
algorithm~\citep{ajanthan2017efficient}. As a consequence, we provide the first
efficient algorithm to compute an upper bound of the log-partition function of
dense CRFs. This provides complementary information to the popular mean-field
inference algorithm for dense CRFs, which computes a lower bound on the
log-partition ~\citep{koltun2011efficient}. Fourthly, we obtain a good 
submodular extension for higher-order Potts model based on an accurate LP
relaxation. Higher-order Potts model is a generalisation of the pairwise Potts
model, and helps to capture interesting properties of the image that cannot be
done using pairwise models~\citep{vineet2014filter, kohli2007p3}. We show that our upper-bounds on synthetic problems are comparable to those from tree reweighted message passing (TRW)
~\citep{wainwright2005new} for the case of sparse CRFs. Unlike our approach,
TRW is computationally infeasible for dense CRFs, thereby limiting its use in
practice. Using pairwise dense CRF models, we perform stereo matching on standard
data sets and obtain better results than \citep{koltun2011efficient}. We also perform semantic segmentation on the MSRC-21 dataset

The complete code is available at \url{https://github.com/pankajpansari/denseCRF}.

>>>>

In this work, we establish a hitherto unknown connection between the submodular
extension of the Potts model proposed by Zhang et al.\citep{zhang2015higher}, and the
objective function of an accurate linear programming (LP) relaxation of the
corresponding MAP estimation problem~\citep{kleinberg2002approximation}. Specifically, the Lovasz extension of a submodular extension can be shown to be an objective function for the LP relaxation. This
connection has four important practical consequences. First, it establishes
the optimality of the submodular extension of the Potts model, via the tightest LP relaxation
under UGC-hardness assumptions. Second, it provides an
accurate submodular extension of the hierarchical Potts model, via the LP
relaxation of the corresponding MAP estimation problem proposed
by Kleinberg and Tardos \citep{kleinberg2002approximation}. Since any metric can be accurately
approximated as a mixture of hierarchical Potts
models~\citep{bartal1996probabilistic, bartal1998approximating}, this result
also provides a computationally feasible algorithm for estimating the marginals
for metric labeling. Third, it establishes the equivalence between the
subgradient of the LP relaxation and the conditional gradient of the problem of
minimising the upper bound of the log-partition. This allows us to employ the
widely used dense CRF, since the subgradient of its LP relaxation can be
efficiently computed using a recently proposed modified Gaussian filtering
algorithm~\citep{ajanthan2017efficient}. As a consequence, we provide the first
efficient algorithm to compute an upper bound of the log-partition function of
dense CRFs. This provides complementary information to the popular mean-field
inference algorithm for dense CRFs, which computes a lower bound on the
log-partition ~\citep{koltun2011efficient}. Fourth, we obtain an accurate 
submodular extension for a higher-order diversity model based on an LP
relaxation. Higher-order models can capture interesting properties of the image that cannot be
done using pairwise models~\citep{vineet2014filter, kohli2007p3}. We show that our upper-bounds on synthetic problems are comparable to those from tree reweighted message passing (TRW)
~\citep{wainwright2005new} for the case of sparse CRFs. Unlike our approach,
TRW is computationally infeasible for dense CRFs, thereby limiting its use in
practice. Using pairwise dense CRF models, we perform stereo matching on standard
data sets and obtain better results than \citep{koltun2011efficient}. We also perform semantic segmentation on the MSRC-21 dataset using a combination of dense pairwise and higher-order diversity model. The complete code is available at \url{https://github.com/pankajpansari/denseCRF}.
